HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
%\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are commonly words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
\XXX{Do we want to cut the following shorter?}
However, 
their focus on verb argument structures misses many semantic phenomena
(such as inter-clause linkage and nominal argument structures) and thus they only provide
a limited perspective on the semantic similarity between the translation and reference.
Also, assigning semantic structure to an MT output, especially a poor one,
is difficult and arguably ill-defined.

@@

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}) and highlight its benefits over HMEANT
(\secref{sec:hmeant_comp}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments}) document the
efficiency (time of annotation) and inter-annotator agreement scores for HUME.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.45\textwidth]{ucca-tree-v2.png}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.45\textwidth]{ucca-tree-mteval-v2.png}
    \end{center}
  \caption{\label{fig:hume_tree_v2}
     HUME annotation of an UCCA tree with a word aligned example translation shown below. 
Atomic units are labelled using traffic lights and structural nodes are marked A or B.}
\end{figure}
% Ondrej removes the following, he thinks that errors are not supposed to be
% propagated in HMEANT either:
%In HMEANT, it is not clear whether errors should be propegated up the SRL hierarchy.

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
\XXX{Do we want to cut the following shorter?}
However, 
their focus on verb argument structures misses many semantic phenomena
(such as inter-clause linkage and nominal argument structures), providing
only
a limited perspective on the semantic similarity between the translation and reference.
Also, assigning semantic structure to an MT output, especially a poor one,
is difficult and arguably ill-defined.

@@

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments}) document the
efficiency (time of annotation) and inter-annotator agreement scores for HUME.
Finally, the differences from HMEANT are discussed 
(\secref{sec:hmeant_comp}).

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.35\textwidth]{ucca-tree-v2.png}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.35\textwidth]{ucca-tree-mteval-v2.png}
    \end{center}
  \caption{\label{fig:hume_tree_v2}
     HUME annotation of an UCCA tree with a word aligned example translation shown below. 
Atomic units are labelled using traffic lights and structural nodes are marked A or B.}
\end{figure}
% Ondrej removes the following, he thinks that errors are not supposed to be
% propagated in HMEANT either:
%In HMEANT, it is not clear whether errors should be propegated up the SRL hierarchy.
